% Make sure that the page counter is correct
\clearpage

% Theme
\theme{Free Cooling}\label{theme:free}

\publication{Mikko Pervilä, Jussi Kangasharju}
% Title
{Running Servers around Zero Degrees}
% Publication
{In ACM \textit{SIGCOMM Computer Communication Review}, Volume 41, Issue 1. ACM, 2011, pp.
96-101, DOI \url{http://dx.doi.org/10.1145/1925861.1925877}.}
% Copyright
{\copyrightACM{2011}}
% Contribution
{I did the major parts of the work alone. Prof. Kangasharju supervised my
work and did minor editing of the text. Figure 2 in was also done by him. I
had some help in the physical construction phases as indicated by the
acknowledgment section. Otherwise, the installation, design of the
experiments, analysis of the results, the text, and figures were done by
me.}
\label{pub:zero}
\includepaper[10mm]{../ACM_CCR_201009/green08t-pervila.pdf}{../ACM_CCR_201009/green08t-pervila.pdf}

% insert page break to publication list
\addtocontents{pub}{\protect\newpage}
% insert page break to table of contents
\addtocontents{toc}{\protect\newpage}

% Theme
\theme{Air Stream Containment}\label{theme:air}

\publication{Mikko Pervilä, Jussi Kangasharju}
% Title
{Cold Air Containment}
% Publication
{In \textit{Proc. 2nd ACM SIGCOMM workshop on Green networking (GreenNet
2011)}. ACM, 2011, pp. 7--12, DOI \url{http://dx.doi.org/10.1145/2018536.2018539}.}
% Copyright
{\copyrightACM{2011}}
% Contribution
{I did the major parts of the work alone. Mikko Rantanen designed and
implemented the power measurement solution described in Sect. 3.1 of the
publication. Prof. Kangasharju supervised my work and did minor editing of the
text. Figure 2 was done according to my specifications by Janne Ahvo and used
with permission. I had some help in the physical construction phases as
indicated by the acknowledgment section.  Otherwise, the design of the
experiments, hardware choices, analysis of the results, writing, and figures
were done by me.}
\label{pub:cac}
\includepaper[10mm]{../SIGCOMM_Green_2011/green12t-pervila.pdf}{../SIGCOMM_Green_2011/green12t-pervila.pdf}


\publication{Mikko Pervilä, Mikko Rantanen, Jussi Kangasharju}
% Title
{Implementation and Evaluation of a Wired Data Center Sensor Network}
% Publication
{In \textit{Energy Efficient Data Centers}, LNCS Vol.7396, pp. 105--116, DOI
\url{http://dx.doi.org/10.1007/978-3-642-33645-4_10}.}
% Copyright
{Copyright \copyright\hspace{2pt} 2012 Springer Berlin Heidelberg. Reprinted
with permission.}
% Contribution
{The design and installation of the wired sensor network was performed as
joint work with Mikko Rantanen. Prof. Kangasharju did minor edits of the text.
Otherwise, the concepts, design of the experiments, analysis of the results,
writing, and figures were mine.}
\label{pub:sensors}
\includepaper[10mm]{../e-Energy_E2DC_2012/pervila.pdf}{../e-Energy_E2DC_2012/pervila.pdf}



\publication{Mikko Pervilä, Jussi Kangasharju}
% Title
{Underfloor Air Containment}
% Publication
{In \textit{Proc. 2nd IEEE Online Conference on Green Communications
(GreenComm 2013)}. IEEE, 2013.}
% Copyright
{\copyrightIEEE{2013}}
% Contribution
{I did the major parts of the work alone. Prof. Kangasharju supervised my work
and did minor editing of the text. He also did a part of the analysis
regarding the GHG emissions of the entire ICT field mentioned in paragraph 1
of the introduction. I had some help in the physical construction phases as
indicated by the acknowledgment section.  Otherwise, the concepts, hardware
choices, design of the experiments, analysis of the results, writing, and
figures were done by me.}
\label{pub:uac}
\includepaper[10mm]{../OnlineGreenComm_2013/article.pdf}{../OnlineGreenComm_2013/article.pdf}

% insert page break to publication list
\addtocontents{pub}{\protect\newpage}

% Theme
\theme{Harvesting Heat}\label{theme:harvesting}

\publication{Mikko Pervilä, Lassi Remes, Jussi Kangasharju}
% Title
{Harvesting Heat in an Urban Greenhouse}
% Publication
{In \textit{Proceedings of the first workshop on Urban networking - UrbaNe
'12}. ACM, 2012, pp. 7--12, DOI
\url{http://dx.doi.org/10.1145/2413236.2413239}.}
% Copyright
{\copyrightACM{2012}}
% Contribution
{Lassi Remes chose the initial set of the plants, planted them with his
spouse, and later advised on the use of pesticides \& fertilizers. He also
judged which plants survived the winter (not included in this paper). A number
of volunteer workers helped in watering the plants. Prof. Kangasharju did
some minor edits of the final text. Timo Ojanen advised on the design of the
greenhouse, and a paid worker did more than half of the construction.
Otherwise, the idea, design of the experiments, analysis of the results,
writing, figures, and further projections were done by me.}
\label{pub:greenhouse}
\includepaper[10mm]{../URBANE_2012/urban304-pervila.pdf}{../URBANE_2012/urban304-pervila.pdf}

